\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Ilia} % Your first name
\familyname{Egorov} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Resume}
% \address{30 22 Mira}{Zarechny, Penzenskaya oblast 442960}
\mobile{+357 97719018}
\email{IEgorov.BH@gmail.com}
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

Throughout my career, I've developed a keen interest in A/B tests, product management, and how my projects impact product and business metrics. I'm passionate about collaborating with cross-functional teams to translate data-driven insights into meaningful product features and improvements that drive business growth.

\section{WORK EXPERIENCE}
\cventry{2021--}{Analytics Team Lead}{Veraxen. Game development company}{Cyprus}{}{
	\begin{itemize}
		\item Management of data analyst, scientist and engineer team of 10 specialists
		\item Built a process of short-term (Scrum) and long-term (quarter) planning, performance review and individual development plan of the team
		\item Improving collaboration between data analysts and scientists with stakeholders
		\item Build the process of conducting, analyzing experiments (a/b tests). The number of experiments was increased by 20 times
		\item Made about 30 different dashboards and reports in the BI system. A new BI system  increased the time of making decisions by stakeholders
		\item Created a DWH, modeled the main domain of the business, which increased the speed of adhoc analysis, self service BI
		\item Maintenance of GCP solution. Optimization of costs and performance of queries
		\item Created an infrastructure for DWH, ML models, experiments, BI. (BigQuery, dbt, airflow, airbyte, growthbook, mlflow, docker)
		\item Developed predictive models for product purposes (classic ML)
	\end{itemize}
}

\cventry{2021}{Product analyst}{Flo health. Women health application}{Remote}{}{
	Full stack product development analytical support in the commercial stream from an idea to delivery in the production. 
}

\cventry{2019--2021}{Product data  analyst}{Exness}{Cyprus}{}{
	Data analysis, data engineering
	\begin{itemize}
		\item Ad-hoc analysis by SQL (DWH Vertica, Amplitude)
		\item Development of corporate metrics and KPIs map, analysis and forecasting. (Tableau)
		\item BI layer datamarts developing (DWH Architecture)
		\item A/B tests recommendations and statistical analysis of the results (statistics/python).
		\item Hiring, onboarding of new data analysts 
		\item Project management (lightweighted Prince2 framework)
	\end{itemize}
}

\cventry{2018--2019}{Data analyst}{Arbina. Startup. The main product is a pixel coloring app (1M DAU)}{}{}{
	\begin{itemize}
		\item Ad-hoc analysis by python/pandas, MongoDB, csv-files.
		\item Regular reports and alerts system with product metrics (LTV, conversion, retention, ARPU, MAU) by backend python/flask, REST API, docker
		\item ETL from Hadoop/Hbase cluster to MongoDB by Spark/Java
		\item AppStore, googlePlay parsing and integration for the reporting system by python, beautifulSoup, docker
	\end{itemize}
}

\cventry{2016--2018}{Analyst}{Vigrom corp. Game development company}{}{}{ Promotion of data-driven approach in the company. 
	\begin{itemize}
		\item Ad-hoc analysis by SQL, python/pandas, Postgresql.
		\item Regular BI reports by redash, python/flask/dash/plotly
		\item A/B tests recommendations and statistical analysis of the results (statistics/python).
		\item Development of corporate metrics and KPIs map, analysis and forecasting. LTV, conversion rates, retention, ARPPU, MAU, ROI, ...
	\end{itemize}
}	

\cventry{2010--2015}{C++ Developer}{Companies(ANTEsoft, Nagradion)}{Penza}{}{Developing efficient numerical algorithms and methods for calculation of the physical model}

\section{EDUCATION}
\cventry{2009--2015}{Master of Physics}{The Penza State University}{Penza, Russia}{GPA = 5.0}{}
\cventry{2013--2014}{Research scientific training}{The Karlsruhe Institute of Technology}{Karlsruhe, Germany}{}{Exploring microscopic defects within the material of superconducting qubits}  % Arguments not required can be left empty


\section{KEY SKILLS AND COMPETENCIES}

{BigQuery, SQL, dbt, python, pandas, ml, tensorflow, mlflow, numpy, scipy, sklearn, matlab, plotly/dash, redash, tableau, amplitude, looker, docker, Git}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{LANGUAGES}

\cvitemwithcomment{English}{Upper intermediate}{}
\cvitemwithcomment{German}{Basic}{}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

%\section{Interests}
%
%\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
%
%\cvlistdoubleitem{Data science}{Machine learning}

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%----------------------------------------------------------------------------------------

\end{document}